Bird beak's elaboration and innovation

### 2022-06-10 Analysis/03-Elaboration_innovation_analysis.Rmd
Update 03-Elaboration_innovation_analysis.Rmd

```{r, echo = FALSE, eval = FALSE}
## Getting the plotting data
ploting_data <- list("median_elaborations" = apply(get.disparity(get.subsets(results$super_results_phylo$position, subsets = "phylogeny"), concatenate = FALSE)[[1]], 1, median),
                     "median_innovations"  = apply(get.disparity(get.subsets(results$super_results_phylo$distance, subsets = "phylogeny"), concatenate = FALSE)[[1]], 1, median),
                     "distances_to_centre" = get.disparity(dispRity(get.subsets(superorder_shapespace, subsets = "phylogeny"), metric = centroids, centroid = 0)),
                     "consensus_tree"      = tree)

## Get the data at the macro level (with no missing data)
get.macro.projection <- function(data, what) {
    if(what == "centroids") {
        ## Measuring the centroid distances
        data <- dispRity(data, metric = dispRity::centroids)
    } else {
        data <- data[[what]]
    }
    ## Getting all the species
    all_species <- apply(get.disparity(get.subsets(data, subsets = "phylogeny"), concatenate = FALSE)[[1]], 1, median)
    ## Getting the species that have a projection on their own group
    macro_level <- apply(do.call(rbind, get.disparity(get.subsets(data, subsets = names(size.subsets(data))[-n.subsets(data)]), concatenate = FALSE)), 1, median)
    ## Replacing the species that have their own group
    all_species[match(names(macro_level), names(all_species))] <- macro_level
}

>>>>

```{r, echo = FALSE, eval = FALSE}
## Getting the plotting data
ploting_data <- list("median_elaborations" = apply(get.disparity(get.subsets(results$super_results_phylo$position, subsets = "phylogeny"), concatenate = FALSE)[[1]], 1, median),
                     "median_innovations"  = apply(get.disparity(get.subsets(results$super_results_phylo$distance, subsets = "phylogeny"), concatenate = FALSE)[[1]], 1, median),
                     "distances_to_centre" = get.disparity(dispRity(get.subsets(superorder_shapespace, subsets = "phylogeny"), metric = dispRity::centroids, centroid = 0))[[1]],
                     "consensus_tree"      = tree)

## Get the data at the macro level (with no missing data)
get.macro.projection <- function(data, what) {
    if(what == "centroids") {
        ## Measuring the centroid distances
        data <- dispRity(data, metric = dispRity::centroids)
    } else {
        data <- data[[what]]
    }
    ## Getting all the species
    all_species <- apply(get.disparity(get.subsets(data, subsets = "phylogeny"), concatenate = FALSE)[[1]], 1, median)
    names(all_species) <- rownames(get.subsets(data, subsets = "phylogeny")$matrix[[1]])
    ## Getting the species that have a projection on their own group
    macro_level <- apply(do.call(rbind, get.disparity(get.subsets(data, subsets = names(size.subsets(data))[-n.subsets(data)]), concatenate = FALSE)), 1, median)
    names(macro_level) <- unlist(lapply(lapply(get.subsets(data, subsets = names(size.subsets(data))[-n.subsets(data)])$subsets, `[[`, "elements"), function(X, matrix) rownames(matrix)[X], matrix = data$matrix[[1]]))
    ## Replacing the species that have their own group
    all_species[match(names(macro_level), names(all_species))] <- macro_level
    return(all_species)
}
